\thetitle\\ \vspace{0.2em} \LARGE{On The Inadequacy of Uniform Modeling for WLAN Workloads}

### 2008-01-20 models.tex
Finally tweaked the models & properties tables to satisfaction.

\begin{tabular}{|c|l|p{5in}|}
\multicolumn{1}{c}{\textbf{Behavior}} &
\multicolumn{1}{c}{\textbf{Model}} &
\multicolumn{1}{c}{\textbf{Description}} \\
\hline
\multirow{3}[13]{*}{Network}
\bigstrut & \multirow{1}{*}[-0.05em]{\textbf{T}race} &
Mapping of flow end-points to wireless nodes taken directly from trace data. \\
\cline{2-3}
\bigstrut & \multirow{1}{*}[-0.05em]{\textbf{M}arginal} &
Use marginal empirical distributions from trace. \\
\cline{2-3}
\bigstrut & \multirow{1}{*}[-0.05em]{\textbf{S}ynthetic} &
Use synthetic distributions \textit{\`a la} Hern\'andez-Campos~\cite{Hernandez06:wlan-traffic}. \\
\cline{2-3}
\bigstrut & \multirow{1}{*}[-0.05em]{\textbf{U}niform} &
Both end-points are uniformly randomly chosen from all of the wireless nodes. \\
\hline
\multirow{2}[11]{*}{Flow}
\bigstrut & \multirow{1}{*}[-0.05em]{\textbf{T}race} &
Each flow has the actual start time, end time, total data sent, and number of packets from the trace. \\
\cline{2-3}
\bigstrut & \multirow{1}{*}{\textbf{P}roportional} &
Byte count taken from trace; sizes and intervals are CBR or VBR, on a per-flow basis. \\
\cline{2-3}
\bigstrut & \multirow{1}{*}{\textbf{U}niform} &
All flows have the same duration, volume, packet rate, and data rate as the trace average. \\
\hline
\multirow{2}[11]{*}{Packet}
\bigstrut & \multirow{1}{*}[-0.05em]{\textbf{T}race} &
The sequence of packet sizes and inter-transmission intervals is taken directly from the trace. \\
\cline{2-3}
\bigstrut & \multirow{1}{*}[-0.05em]{\textbf{S}ample} &
Packets sizes and intervals are randomly drawn from per-flow empirical distributions (VBR). \\
\cline{2-3}
\bigstrut & \multirow{1}{*}[-0.05em]{\textbf{U}niform} &
Packets sizes are uniform and the inter-packet interval is constant (CBR). \\
\hline
\end{tabular}

>>>>

\begin{tabular}{|c|c|p{4.3in}|}
\multicolumn{1}{c}{\textbf{Level}} &
\multicolumn{1}{c}{\textbf{Model}} &
\multicolumn{1}{c}{\textbf{Description}} \\[2pt]
\hline
\multirow{8}{*}[3.0pt]{Node}
& \multirow{1}{*}[-0.05em]{Individual} &
\begin{minipage}[l]{4.3in}
\vspace{2pt}
each node corresponds to a specific trace node with associated trace flows \\
session start time assigned from trace \\
overrides all distributions with per-node versions
\vspace{2pt}
\end{minipage} \\
\cline{2-3}
& \multirow{1}{*}[-0.05em]{Nonparametric} &
\begin{minipage}[l]{4.3in}
\vspace{2pt}
generic flows assigned to nodes by sampling \\
session start time assigned from pool of start times
\vspace{2pt}
\end{minipage} \\
\cline{2-3}
& \multirow{1}{*}[-0.05em]{Parametric} &
\begin{minipage}[l]{4.3in}
\vspace{2pt}
generic flows assigned to nodes according to BiPareto model \\
session start time randomly chosen from viable range
\vspace{2pt}
\end{minipage} \\
\cline{2-3}
& \multirow{1}{*}[-0.05em]{Uniform} &
\begin{minipage}[l]{4.3in}
\vspace{2pt}
all nodes have average number of generic flows \\
session start times uniformly cover viable range
\vspace{2pt}
\end{minipage} \\
\hline
\multirow{11}{*}[2.5pt]{Flow}
& \multirow{1}{*}[-0.05em]{Individual} &
\begin{minipage}[l]{4.3in}
\vspace{2pt}
each flow corresponds to a specific trace flow with an associated packet trace \\
flow size \& start time taken from trace \\
overrides distributions of size/interval packet behaviors with flow-specific versions
\vspace{2pt}
\end{minipage} \\
\cline{2-3}
& \multirow{1}{*}[-0.05em]{Nonparametric} &
\begin{minipage}[l]{4.3in}
\vspace{2pt}
flow size is sampled from inherited distribution of flow sizes \\
start time relative to previous session flow sampled from inherited distribution \\
inherits distributions of size/interval packet behaviors from destination node
\vspace{2pt}
\end{minipage} \\
\cline{2-3}
& \multirow{1}{*}[-0.05em]{Parametric} &
\begin{minipage}[l]{4.3in}
\vspace{2pt}
flow size is sampled from BiPareto model fitted to inherited distribution \\
start time relative to previous session flow sampled Lognormal fitted to inherited \\
inherits distributions of size/interval packet behaviors from destination node
\vspace{2pt}
\end{minipage} \\
\cline{2-3}
& \multirow{1}{*}[-0.05em]{Uniform} &
\begin{minipage}[l]{4.3in}
\vspace{2pt}
all flows have size equal to inherited mean \\
average inter-flow interval used between all flows \\
inherits distributions of size/interval packet behaviors from destination node
\vspace{2pt}
\end{minipage} \\
\hline
\multirow{5}{*}[2.5pt]{Packet}
& \multirow{1}{*}[-0.05em]{Individual} &
\begin{minipage}[l]{4.3in}
\vspace{2pt}
each packet corresponds to a specific trace packet
\vspace{2pt}
\end{minipage} \\
\cline{2-3}
& \multirow{1}{*}[-0.05em]{Nonparametric} &
\begin{minipage}[l]{4.3in}
\vspace{2pt}
packet sizes and intervals are sampled from inherited distributions
\vspace{2pt}
\end{minipage} \\
\cline{2-3}
& \multirow{1}{*}[-0.05em]{Parametric} &
\begin{minipage}[l]{4.3in}
\vspace{2pt}
packet sizes and intervals are drawn from inherited parametric distributions
\vspace{2pt}
\end{minipage} \\
\cline{2-3}
& \multirow{1}{*}[-0.05em]{Uniform} &
\begin{minipage}[l]{4.3in}
\vspace{2pt}
all packet sizes and inter-packet intervals are equal to inherited mean
\vspace{2pt}
\end{minipage} \\
\hline
\end{tabular}
